---
title: "Homework 6"
author: "Ben Pfingston, Leah Peterson, and Alexus Rock"
format: pdf
editor: visual
fig-width: 6.5
fig-height: 8
execute:
  echo: FALSE
warning: FALSE
bibliography: hw6_bib.bib
---

```{r}
#loading in packages

library(tidyverse)
library(rio)
library(here)
library(ggplot2)
library(knitr)
```

```{r}
#loading in data

star <- import(here("data", "star.csv"))
```

We are using R for this assignment [@rcite]. To import the data, @herecite created a package that helps us find the file we want to use in the assignment. Additionally, we are using the tidyverse to help organize our data [@tidycite]. Then, to create the figure, @ggcite made a comprehensive package that allows us to make graphs and figures with multiple different formating options.

\newpage

```{r}
star %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss, na.rm = TRUE),
            math_sd = sd(tmathss, na.rm = TRUE),
            rdg_mean = mean(treadss, na.rm = TRUE),
            rdg_sd = sd(treadss, na.rm = TRUE)) %>% 
  kable(digits = 2)


```

This is a table of the summary statistics for the mean of total math score, the standard deviation of total math score, the mean of total reading score, and the standard deviation of total reading score by sex and by if free reduced lunch (frl) is received.

\newpage

```{r}

ggplot(star, aes(totexp, tmathss)) +
  geom_point(color = "grey", size = 0.5) +
  geom_smooth(aes(color = frl), method = "lm") +
  labs(x = "Teacher Experience (years)",
       y = "Total Math Scale Score",
       title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced lunch price status")


```

This is a plot of the relationship between teacher experience and student math scores for students who receive free/reduced lunch and those that do not.

\newpage

# References
